---
title: "DMR Landings"
output: github_document
---

A lightweight R package to simplify the import of [DMR annual commercial landings data](https://mainedmr.shinyapps.io/Landings_Portal/).  As described at the portal, the data are served in two forms:

+ "Historic" annual statewide totals per species (1880-2019)

+ "Modern" annual per-port totals per species (2008-2024)

We provide two more forms:

+ "Merged" a simple merging of the two where "historic" ports are assigned the value of "ME".  This form likely has limited value.

+ "Annualized" a simple state wide total per species per year.  This may be more useful than "merged".

The package should be updated every spring when [DMR updates the data source](https://mainedmr.shinyapps.io/Landings_Portal/).

# Requirements

- [R v4.3+](https://www.r-project.org/)

- [readr](https://CRAN.R-project.org/package=readr)

- [dplyr](https://CRAN.R-project.org/package=dplyr)


# Installation

```
remotes::install("BigelowLab/dmrlandings")
```

# Usage

```{r}
suppressPackageStartupMessages({
  library(dmrlandings)
  library(dplyr)
})
```

```{r}
x = read_dmr_landings("modern") |>
  glimpse()
```


```{r}
x = read_dmr_landings("historic") |>
  glimpse()
```


```{r}
x = read_dmr_landings("annualized") |>
  glimpse()
```
